% vim:ft=tex:
%
\documentclass[12pt]{letter} % https://en.wikibooks.org/wiki/LaTeX/Letters 

\usepackage{fancyhdr}
\usepackage{textcase}
\usepackage{relsize}
\usepackage{amsmath}
\usepackage{changepage}
\usepackage{setspace}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage[margin=1in, bottom=0in]{geometry}

% get rid of bullet separation
\setlist{nosep} % https://tex.stackexchange.com/questions/10684/vertical-space-in-lists 

%\setlength{\headheight}{2pt}
\pagestyle{plain}

\newcommand{\email}[1]{\href{mailto:#1}{#1}}


% Letter stuff
\signature{Jason Schuchardt}
\address{4000 Randall Avenue \\ St.\ Louis Park MN, 55416}

% Specific template things

\newcommand{\companyname}{Some Company/Lab, TODO}
\newcommand{\companyinfo}{\companyname \\ Company Street Address, TODO \\ Company City and Zip, TODO}
\newcommand{\recruitername}{Recruiter Name, TODO}
\newcommand{\jobdiscoveredon}{TODO}
\newcommand{\positionname}{TODO}

\begin{document}


\begin{letter}{}
\companyinfo

\opening{Dear \recruitername,}

My name is Jason Schuchardt. I'm excited to be applying for the open \positionname\ role at \companyname.
After reviewing your job description, I am confident that I have the necessary skills and expertise to 
succeed in the position. 

I am an adaptable recent college graduate graduating with an M.S.\ in Mathematics from Yale University.
While working over the summers I have accrued work experience in both research and programming.
Last summer I worked
as an undergraduate researcher in mathematics at Yale,
and the summer before I worked as a lab programmer at the 
Laboratory of Neurocognitive Development at the University of Pittsburgh. From this experience I have
acquired valuable technical skills such as (TODO, elaborate on technical skills with reference to the job
posting). In both my academic and professional life, I have been consistently praised as a quick learner by
my professors, peers and mentors.
(TODO is this really necessary xD I feel like it's such bullshit xD particularly
since you don't hear that from your profs at yale xP) 
Whether working on academic, extracurricular, or professional projects, I apply proven problem-solving, 
research, and technical skills, which I hope to use in the capacity of a \positionname at your lab. % TODO
% change lab to company or organization or whatever is applicable

After reviewing my resume, I hope you will agree that I am the type of competent and competitive candidate 
you are looking for. I look forward to elaborating on how my specific skills and abilities will benefit your
organization. Please contact me at (412) 728-8774 or via email at 
\email{jason.sch@aya.yale.edu} to arrange a convenient meeting time.

Thank you for your consideration, and I look forward to hearing from you soon.

\closing{Sincerely,}
\end{letter}


\end{document}
