\documentclass[11pt]{article}

\usepackage{fancyhdr}
\usepackage{textcase}
\usepackage{relsize}
\usepackage{amsmath}
\usepackage{changepage}
\usepackage{setspace}
\usepackage[margin=1in, bottom=0in]{geometry}

\setlength{\headheight}{2pt}
\pagestyle{fancy}
\fancyhead[l]{\small (412) 728-8774\\ jasonsch.yale@gmail.com}
\fancyhead[c]{\huge \textbf{Jason Schuchardt}}
\fancyhead[r]{\scriptsize \it 
4000 Randall Avenue\\
St. Louis Park, MN 55416
}
\fancyfoot{}

\newcommand{\myrule}[1][.9]{\par\vspace*{-.65\baselineskip}\noindent\hfil\rule{#1\textwidth}{0.4pt}\hfil\par}
\newcommand{\mysechead}[1]{\par\noindent {\large \bf \MakeTextUppercase{#1}}}
\newcommand{\resentry}[2]{\hspace*{.5em}{\bf{#1}}\hfill{\it{#2}}}
\newcommand{\resbody}[1]{\begin{adjustwidth}{1em}{0.5em}{\fontsize{10pt}{1em}\selectfont
\it
#1\par}\end{adjustwidth}}

\begin{document}
\vspace*{-7.0pt}
\mysechead{Education}
\myrule

\noindent
\resentry{M.S., B.S. Mathematics Yale University}{Fall 2014-May 2018}
\resbody{GPA/Major GPA: 3.61/3.85 out of 4.00}\vspace{-5pt}
%\resentry{High School, Graduated Cum Laude from Sewickley Academy}{Fall 2010-Spring 2014}
%\resbody{Final Unweighted GPA: 3.86}
\vspace*{\baselineskip}

\mysechead{Technical Skills}
\myrule

\noindent
\begin{tabular}{lp{10cm}}
  Languages & C, C\raise.30ex\hbox{\smaller{\verb!++!}}, C$^\sharp$, Elm, Haskell, Java, Javascript,
    \LaTeX, MATLAB, Perl, Python, R, Ruby, Scheme\\
  DSLs and Data Languages & HTML, CSS, XML, JSON, GLSL, YAML\\
  Frameworks and Libraries & Ruby on Rails, Bootstrap, Yesod, OpenGL, NumPy, pandas\\
  Operating Systems & Linux, Windows, MacOS\\
  Software and Tools & Git, Vim, bash, Eclipse, Visual Studio\\ %, TODO \\
\end{tabular}
\vspace*{\baselineskip}

\mysechead{Work Experience, Projects and Volunteering}
\myrule

\noindent
\resentry{Undergraduate Math Research with SUMRY at Yale}{Summer 2017}
\resbody{I worked in a group of three to understand the structure of subdivisions of simplices with local-$h$ 
zero. Local-$h$ is a combinatorial invariant of subdivisions of simplices introduced by Richard Stanley which
has received increased attention lately due to connections with intersection cohomology of toric varieties.}
\resentry{MIT Web Development Contest}{January 2016}
\resbody{With a friend from MIT I wrote a web app whose purpose was to allow users to form groups and 
schedule events and activities using Ruby on Rails, Bootstrap, and Angular-js.
}
\resentry{Intern at the Laboratory of Neurocognitive Development}{Summer 2016}
\resbody{
  Worked on a variety of daily tasks for the lab. The large project we worked on at the time was updating
  the database interface. We used an Elm frontend on top of a PostgREST backend.
}
\resentry{Counselor at the Ross Mathematics Program}{Summer 2015}
\resbody{
Mentored high school students as they learned number theory and completed problem sets. 
}
\resentry{Volunteer Web Developer for MMATHS Project}{Fall 2014}
\resbody{A friend and I volunteered to write a web app using Ruby on Rails to allow other volunteers to
submit problems for the MMATHS competition. Among many other things, I used the MathJax library to
show problem previews for
problems written in \LaTeX, and created a page to edit and preview tests.}
\resentry{Junior Counselor at the Ross Mathematics Program}{Summer 2014}
\resbody{Having attended as a first year in Summer 2013, I was asked to return as a JC. I worked on finishing
sets from my first year, graded first years' sets, and helped guide first years without giving
away answers.}
\resentry{Volunteer at the Laboratory of Neurocognitive Development}{Spring 2014}
\resbody{Volunteered for two weeks (60\raise.4ex\hbox{\smaller{+}} hours) at the LNCD at
the University of Pittsburgh for my senior project. I worked on the database interface for the lab's subject information (which was written with Mojolicious, Bootstrap, and AngularJS), a working memory task for a study written in MATLAB, as well as numerous smaller projects involving mostly bash scripting and data visualization with the aid of R.}
\resentry{Private Math Tutor}{Fall 2013-Spring 2014}\\
\resentry{Mathcounts Volunteer Coach}{Fall 2010-Spring 2014}\\

\mysechead{Relevant Coursework}
\myrule

\noindent
\resentry{Yale University}{Fall 2014-Spring 2018}
\resbody{
  %Vector Calculus and Linear Algebra I and II (MATH 230,231),
  %Mathematical Problem Solving (MATH 199),
  %Number Theory (MATH 354),
  %Introduction to Computer Science (CPSC 201),
  Data Structures and Programming Techniques (CPSC 223)
}
%\resentry{University of Pittsburgh}{Fall 2013-Spring 2014}
%\resbody{Mutivariable Calculus, Complex Variables}
\vspace*{\baselineskip}

\mysechead{Extracurricular Activities and Projects}
\myrule
    
\noindent
\resentry{High School Programming Club}{Fall 2010-Spring 2014}
\resbody{President from Fall 2011 to Spring 2014. In the 2013-2014 school year,
we wrote a video game in $\textup{C}^\sharp$. Since this was an educational project,
I wrote most of the physics, graphics, math, and game libraries from scratch starting from
the .NET Framework and Windows Forms.}
\resentry{Western PA ARML}{Fall 2008-Spring 2014}\\

\mysechead{Awards and Accomplishments}
\myrule

\noindent
%TODO: Putnam
\resentry{Putnam Competition}{Winter 2014, 2015, 2016, 2017}
\resbody{
  Rank or rank group as currently known to me: 172,-,H,171\\
  (Detailed score and rank information is not released publicly)
}
\resentry{USAMO Qualifier (Score: 14)}{Spring 2014}\\
\resentry{High School Senior Math Award}{Spring 2014}\\
\resentry{High School Senior Computer Science Award}{Spring 2014}\\
%\resentry{Gannon University Programming Contest $1^{\text{st}}$ Place}{Spring 2011}\\
\resentry{Yale Science \& Engineering Association}{Spring 2011}
\resbody{Most Outstanding Exhibit in Computer Science, Engineering,
Physics or Chemistry at the Pittsburgh Regional Science \& Engineering Fair}

\end{document}

