\documentclass[11pt]{article}

\usepackage{fancyhdr}
\usepackage{textcase}
\usepackage{relsize}
\usepackage{amsmath}
\usepackage{changepage}
\usepackage{setspace}
\usepackage{enumitem}
\usepackage[margin=1in, bottom=0in]{geometry}

% get rid of bullet separation
\setlist{nosep} % https://tex.stackexchange.com/questions/10684/vertical-space-in-lists 

\setlength{\headheight}{2pt}
\pagestyle{fancy}
\fancyhead[l]{\small (412) 728-8774\\ jason.sch@aya.yale.edu}
\fancyhead[c]{\huge \textbf{Jason Schuchardt}}
\fancyhead[r]{\scriptsize \it 
4000 Randall Avenue\\
St. Louis Park, MN 55416
}
\fancyfoot{}

\newcommand{\myrule}[1][.9]{\par\vspace*{-.65\baselineskip}\noindent\hfil\rule{#1\textwidth}{0.4pt}\hfil\par}
\newcommand{\mysechead}[1]{\par\noindent {\large \bf \MakeTextUppercase{#1}}}
\newcommand\myfill{\leaders\hbox{$\cdot$}\hfill}
\newcommand{\resentry}[2]{\hspace*{.5em}{\bf{#1}}\myfill{\it{#2}}}
\newcommand{\resbody}[1]{\begin{adjustwidth}{1em}{0.5em}{\fontsize{10pt}{1em}\selectfont
\it
#1\par}\end{adjustwidth}}
\newcommand\resitem{\item 
    %\fontsize{10pt}{1em}\selectfont
    \it
    }
\newcommand{\resbodybullets}[1]{
  {
    \setstretch{0.9}
    \begin{itemize}
        {#1}
    \end{itemize}
  }
}


\begin{document}
\setlength{\parindent}{0pt}
\vspace*{-7.0pt}
\mysechead{Education}
\myrule

\noindent
\resentry{M.S., B.S. Mathematics Yale University}{Fall 2014-May 2018}
\resbody{GPA/Major GPA: 3.61/3.85 out of 4.00}\vspace{-5pt}
%\resentry{High School, Graduated Cum Laude from Sewickley Academy}{Fall 2010-Spring 2014}
%\resbody{Final Unweighted GPA: 3.86}
\vspace*{\baselineskip}

\mysechead{Technical Skills}
\myrule

\noindent
\begin{tabular}{lp{10cm}}
  Languages & C, C\raise.30ex\hbox{\smaller{\verb!++!}}, C$^\sharp$, Elm, Haskell, Java, Javascript,
    \LaTeX, MATLAB, Perl, Python, R, Ruby, Scheme\\
  DSLs and Data Languages & HTML, CSS, XML, JSON, GLSL, YAML\\
  Frameworks and Libraries & Ruby on Rails, Bootstrap, Yesod, OpenGL, NumPy, pandas\\
  Operating Systems & Linux, Windows, MacOS\\
  Software and Tools & Git, Vim, bash, Eclipse, Visual Studio\\ %, TODO \\
\end{tabular}
\vspace*{\baselineskip}

\mysechead{Work Experience, Projects and Volunteering}
\myrule

\noindent
\resentry{Undergraduate Math Research with SUMRY at Yale}{Summer 2017}
\resbodybullets{
  \resitem Worked in a group to understand the structure of subdivisions of simplices with local-$h$ 
zero. 
  \resitem Local-$h$ is a combinatorial invariant of subdivisions of simplices introduced by Richard Stanley
    which is connected with the intersection cohomology of toric varieties.
  \resitem Paper in progress.
}
\resentry{MIT Web Development Contest}{January 2016}
\resbodybullets{
  \resitem Wrote a web app with a friend from MIT
  \resitem The app allowed users to form groups and schedule events and activities.
  \resitem Built with Ruby on Rails, Bootstrap, and Angular-js and used Google's Maps API.
}
\resentry{Intern at the Laboratory of Neurocognitive Development}{Summer 2016}
\resbodybullets{ 
  \resitem Worked on a variety of daily tasks for the lab. % TODO: clarify
  \resitem Used Elm to implement a frontend for a PostgREST backend.
}
\resentry{Counselor at the Ross Mathematics Program}{Summer 2015}
\resbodybullets{
  \resitem Mentored high school students as they learned number theory and completed problem sets. 
}
\resentry{Volunteer Web Developer for MMATHS Project}{Fall 2014}
\resbodybullets{
  \resitem Volunteered with a friend to write a web app for the Math Majors of America Tournament for High 
    Schoolers (MMATHS).
  \resitem The app allowed volunteers to submit problems for the MMATHS competition.
  \resitem Used Ruby on Rails, Bootstrap, and MathJax.
}
%show problem previews for
%problems written in \LaTeX, and created a page to edit and preview tests.}
\resentry{Junior Counselor at the Ross Mathematics Program}{Summer 2014}
\resbodybullets{
  \resitem Attended as a first year in Summer 2013 and was asked to return as a JC. 
  \resitem Worked on finishing problem sets from the year before,
  graded first years' sets, and helped guide first years without giving away answers.
}
\resentry{Volunteer at the Laboratory of Neurocognitive Development (LNCD)}{Spring 2014}
\resbodybullets{
  \resitem Volunteered for two weeks (60\raise.4ex\hbox{\smaller{+}} hours) at the LNCD at
    the University of Pittsburgh for my senior project.
  \resitem Worked on the database interface for the lab's subject information, 
    which was built with Mojolicious, Bootstrap, and AngularJS.
  \resitem Wrote a working memory task for a study written in MATLAB.
  \resitem Also worked on 
    numerous smaller projects involving such things as bash scripting and data visualization
    with the aid of R.
}
%\resentry{Private Math Tutor}{Fall 2013-Spring 2014}\\
\resentry{Mathcounts Volunteer Coach}{Fall 2010-Spring 2014}\\

\mysechead{Relevant Coursework}
\myrule

\noindent
\resentry{Yale University}{Fall 2014-Spring 2018}
\resbody{
  %Vector Calculus and Linear Algebra I and II (MATH 230,231),
  %Mathematical Problem Solving (MATH 199),
  %Number Theory (MATH 354),
  %Introduction to Computer Science (CPSC 201),
  Data Structures and Programming Techniques (CPSC 223),
  Systems Programming \& Computer Organization (CPSC 323),
  Design and Analysis of Algorithms (CPSC 365),
  Discrete Mathematics (MATH 244),
  Intro to Functional Analysis (MATH 525),
  Foundations of Algebraic Geometry (MATH 619),
  Quantum Mechanics I \& II (PHYS 508 \& 608)
}
%\resentry{University of Pittsburgh}{Fall 2013-Spring 2014}
%\resbody{Mutivariable Calculus, Complex Variables}
%\vspace*{\baselineskip}
%
%\mysechead{Extracurricular Activities and Projects}
%\myrule
    %
%\noindent
%\resentry{High School Programming Club}{Fall 2010-Spring 2014}
%\resbody{President from Fall 2011 to Spring 2014. In the 2013-2014 school year,
%we wrote a video game in $\textup{C}^\sharp$. Since this was an educational project,
%I wrote most of the physics, graphics, math, and game libraries from scratch starting from
%the .NET Framework and Windows Forms.}
%\resentry{Western PA ARML}{Fall 2008-Spring 2014}\\

\mysechead{Awards and Accomplishments}
\myrule

\noindent
%TODO: Putnam
\resentry{Putnam Competition}{December 2014, 2015, 2016, 2017}
\resbody{
  Highest ranking: Honorable Mention (Top 100 out of 4164 students)
  %Rank or rank group as currently known to me: 172,-,H,171\\
  %(Detailed score and rank information is not released publicly)
}
\resentry{USA Mathematical Olympiad Qualifier (Score: 14)}{Spring 2014}\\
%\resentry{High School Senior Math Award}{Spring 2014}\\
%\resentry{High School Senior Computer Science Award}{Spring 2014}\\
%\resentry{Gannon University Programming Contest $1^{\text{st}}$ Place}{Spring 2011}\\
%\resentry{Yale Science \& Engineering Association}{Spring 2011}
%\resbody{Most Outstanding Exhibit in Computer Science, Engineering,
%Physics or Chemistry at the Pittsburgh Regional Science \& Engineering Fair}

\end{document}

